Update of the ozone dry deposition in the OsloCTM3 v1.0

### 2018-11-21 DryDep_supplement.tex
Found some mistake in the analysis. Re-did the plots, but haven't had the nerve to go through the text again...

\subsection*{S.6 }
\subsubsection*{S.6.1 Normed zonal average ozone dry deposition velocity}
\appendixfigures
\begin{center}
  \includegraphics[height=0.4\textheight, clip, trim={0.7cm 0.7cm 0.7cm 0.55cm}]{pictures/final-norm_total_ozone_drydepvelo}
\end{center}

\subsubsection*{S.6.2 Average ozone dry deposition velocity seperated by land surface type (southern hemisphere)}
\appendixfigures
\begin{center}
  \includegraphics[height=0.4\textheight, clip, trim={0.7cm 0.7cm 0.7cm 0.55cm}]{pictures/final-total_ozone_drydepvelo_monthly_pft_sh}
\end{center}
\end{document}

>>>>

\subsection*{S.6 Normed zonal average ozone dry deposition velocity}
%\subsubsection*{S.6.1 }
\appendixfigures
\begin{center}
  \includegraphics[height=0.4\textheight, clip, trim={0.7cm 0.7cm 0.7cm 0.55cm}]{pictures/final-norm_total_ozone_drydepvelo}
\end{center}

\end{document}
